---
title: "My Website"
---



# Is there any relations between power consumed by each appliances?

```{r, echo=FALSE}
htmltools::includeHTML("eco/plotly.html")
```

I choose the heatmap as the plot is because the dataset after processed is in a strict 8*24 matrix form. We can intuitively see how much electricity they consume and patterns from the color of the light. Judging from the plot, the members in household 4 has 2 breakfast times, 6 am and 8 am. They use a microwave to cook lunch and dinner and entertain after the 2 meals. Their peaks have a continuing relationship.




## Do electric power consumed by appliance varies between seasons?

```{r, echo=FALSE}
htmltools::includeHTML("eco/altair.html")
```

I choose the line chart for the dataset is because there are some null values in folders of appliances. So some arrays with null values need to be removed. There are two dives in September, it may indicate that there were two blackouts in September. There is a decrease in Freezer since December while other appliances don't change a lot, it indicates the in December the area where the house is located is cold enough to preserve stuff that needs to be placed in the refrigerator.